### 2023-06-07 resilience-safe-up.tex
up

\alain{indecidabilite en enlevant une ou des hypotheses: The resilience problem (RP), the bounded resilience problem (BRP)
and the $k$-resilience problem (kRP) are undecidable for WSTS with strong compatibility}
%

@@

Coverability reduce
to resilience when $\Bad = \downarrow \Bad$ and  $\Safe = \uparrow \Safe$.
Indeed $s \to^* \uparrow t$ 
reduces to $(\Safe,\Bad)$-resilience for $\Bad = \downarrow s$ and $\Safe = \uparrow t$.

>>>>

% \alain{indecidabilite en enlevant une ou des hypotheses: The resilience problem (RP), the bounded resilience problem (BRP) and the $k$-resilience problem (kRP) are undecidable for WSTS with strong compatibility}
%

@@

Coverability reduce
to resilience when $\Bad = \downarrow \Bad$ and  $\Safe = \uparrow \Safe$.
Indeed $s \to^* \uparrow t$ 
reduces to $(\Safe,\Bad)$-resilience for $\Bad = \downarrow s$ and $\Safe = \uparrow t$.
Hence, without the completion-post-effective hypothesis, 
{\sc Resilience} is undecidable.
